\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-13 docs/paper/paper.tex
* Few more fixes in the text * Framework for GAN experiments

Additionally, we have used the dataset that has been used in \cite{paper0}. \hl{This dataset contains over 1000 samples. Inputs to this data is .... and outputs are ....} We have only used log of confinement loss as the output. This dataset is referred as \dszero. Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.

@@

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			legend pos=north west,
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
			\addlegendentry{$Proposed$}

@@

		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{../../experiments_pcf2/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
		\addlegendentry{$Proposed$}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/vswavelength134_fold1.txt};
	\addlegendentry{$Proposed$}

@@

	\end{axis}
	\end{tikzpicture}
	\begin{tikzpicture}
	\begin{axis}[
		legend pos=north west,
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.35}$},
		width=0.48\textwidth
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/vswavelength135_fold1.txt};
	\addlegendentry{$Proposed$}

@@

During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(4).
In this subsection we discuss the results of augmenting the real dataset with generated samples. Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the dataset.
This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data. There are several reasons for why our ANN model is driven in the wrong direction. Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data. Furthermore, the generated data might lack realism. Or the sampling strategy adopted is poor. But the most convincing reason is the limited original training dataset size of 336 samples, used to train the WGAN model in the first place. After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.

It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used.

@@

\begin{table}[h]
\begin{tabular}{lllll}
    & dataset size & mini batch size & Time elapsed (sec) \\
Mini batches    &336 + 0 & 8 & 214 & \\
    &336 + 1000 & 8 & 744 & \\
    &336 + 2000 & 16 & 685  & \\ 
    &336 + 3000 & 20 & 861  & \\
\end{tabular}
\begin{tabular}{lllll}
   & dataset size & Time elapsed (sec) \\
Full batch    &336 + 0 &  23 & \\
    &336 + 1000 &  34 & \\
    &336 + 2000 &  45 & \\ 
    &336 + 3000 &  57 & \\
\end{tabular}
\caption{Training performance using Tensorflow(Keras). CPU based training.}
\end{table}
\begin{table}[h]
\begin{tabular}{lllll}
 & dataset size & mini batch size & Time elapsed (sec) \\
Mini batches    & 336 + 0 & 8 & 1315 & \\
    & 336 + 1000 & 8 & 6453  & \\
    & 336 + 2000 & 16 & 4751  & \\ 
    & 336 + 3000 & 20 & 5132 & \\
\end{tabular}
\begin{tabular}{lllll}
   &dataset size & Time elapsed (sec) \\
   Full batch &336 + 0 &  36  & \\
    & 336 + 1000 &  98  & \\
    & 336 + 2000 &  195  & \\ 
    & 336 + 3000 &  336  & \\
\end{tabular}
\caption{Training performance using Pytorch. CPU based training.}
\end{table}

>>>>

Additionally, we have used the dataset that has been used in \cite{paper0}. \hl{This dataset contains over 1000 samples. Inputs to this data is .... and outputs are ....} We have only used log of confinement loss as the output. This dataset is referred as \dszero. Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}. As a final note, the range and domain of these datasets are different; therefore, all comparisons should be drawn within the same dataset.

@@

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth,
			legend pos=south east
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
			\addlegendentry{$Proposed$}

@@

		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth,
		legend pos=south east
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{../../experiments_pcf2/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
		\addlegendentry{$Proposed$}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		legend pos=north east
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/vswavelength134_fold1.txt};
	\addlegendentry{$Proposed$}

@@

	\end{axis}
	\end{tikzpicture}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.35}$},
		width=0.48\textwidth,
		legend pos=north east
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/vswavelength135_fold1.txt};
	\addlegendentry{$Proposed$}

@@

We have performed experiments to showcase the improvement gained by augmenting training samples using a GAN. In Figure ... the results of these experiments has shown. GAN does not only boost the score of the proposed ANN system, but also decreases the MSE on the method proposed in \cite{paper0}. An additional note to take away from this experiment is that the dataset with the least number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table .... This is due the fact that the number of training samples in this dataset is insufficient to train the regressor networks.

\hl{Information about the number of augmented samples.}

The final set of experiments shows the stability that GAN phase adds. In Table ... we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing. It is clear that the GAN phase not only improves the average case but significantly improves the worst case, which is important in a live setting. This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.

@@

\begin{table}
\begin{tabular}{lllll}
    & dataset size & mini batch size & Time elapsed (sec) \\
Mini batches    &336 + 0 & 8 & 214 & \\
    &336 + 1000 & 8 & 744 & \\
    &336 + 2000 & 16 & 685  & \\ 
    &336 + 3000 & 20 & 861  & \\
\end{tabular}
\begin{tabular}{lllll}
   & dataset size & Time elapsed (sec) \\
Full batch    &336 + 0 &  23 & \\
    &336 + 1000 &  34 & \\
    &336 + 2000 &  45 & \\ 
    &336 + 3000 &  57 & \\
\end{tabular}
\caption{Training performance using Tensorflow(Keras). CPU based training.}
\end{table}
\begin{table}
\begin{tabular}{lllll}
 & dataset size & mini batch size & Time elapsed (sec) \\
Mini batches    & 336 + 0 & 8 & 1315 & \\
    & 336 + 1000 & 8 & 6453  & \\
    & 336 + 2000 & 16 & 4751  & \\ 
    & 336 + 3000 & 20 & 5132 & \\
\end{tabular}
\begin{tabular}{lllll}
   &dataset size & Time elapsed (sec) \\
   Full batch &336 + 0 &  36  & \\
    & 336 + 1000 &  98  & \\
    & 336 + 2000 &  195  & \\ 
    & 336 + 3000 &  336  & \\
\end{tabular}
\caption{Training performance using Pytorch. CPU based training.}
\end{table}
